Incentivizing Exploration with Unbiased History

### 2018-11-01 llevel-overview.tex
expected regret -> regret

\section{$L$-level Recommendation Policy}
\label{sec:llevel}
In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ in order to achieve better regret. In Theorem \ref{thm:llevel-1}, we show our $L$-level policy. We can achieve nearly optimal regret $O(T^{1/2} polylog(T))$ with $O(\log\log(T))$ levels.
\begin{theorem}
\label{thm:llevel-1}
For any $L > 3$, we have an $L$-level recommendation policy with expected regret \\$O\left(T^{2^{L-1}/(2^L-1)} polylog(T) \right)$. In particular, we have an $O(\log\log(T))$-level recommendation policy with expected regret $O(T^{1/2} polylog(T))$. 
\end{theorem}

In Theorem \ref{thm:llevel-2}, we show a recommendation policy with instance-dependent regret guarantee. This policy has the same structure as the one in Theorem \ref{thm:llevel-1} but different parameters. Its expected regret depends on $\Delta$ which is the difference between the largest mean and second largest mean of arms and its construction does not depend on $\Delta$. Its regret bound outperforms the one in Theorem \ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$. The only downside is that this policy requires more levels, i.e. $O(\log(T)/\log\log(T))$ levels. It also has the property that each agent observes a good fraction of history till its round.

\begin{theorem}
\label{thm:llevel-2}
 We have an $O(\log(T)/\log\log(T))$-level recommendation policy with expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$. Here $\Delta$ is the difference between the largest mean and second largest mean of arms. The recommendation policy does not depend on $\Delta$. Moreover, agent in round $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$. 
\end{theorem}

@@

Simply generalizing this idea to an $L$-level policy would give us a $S$-ary tree like structure and the first level will have $S^{L-1}$ groups. It incurs an extra $S^{\Omega(L)}$ factor in the expected regret. If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor super poly-logarithmic. If we use $\log(T)/\log\log(T)$ levels as in Theorem \ref{thm:llevel-2}, this factor goes up to polynomial in $T$.

@@

For each level, our $L$-level policy has $S^2$ groups for some $S = \Theta(\log(T))$. The groups in the $l$-th level are labeled as $G_{l,u,v}$ for $u,v\in[S]$. For any $l \in \{2,...,L\}$ and $u,v,w\in [S]$, agents in group $G_{l,u,v}$ see the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level). This connecting structure has three nice properties: \\
(i) The number of groups does not grow with $L$ and stays as $S^2 = \Theta(\log^2(T))$ in each level. Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the expected regret.\\
(ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,S,v}$ (e.g. $G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l-1$ and $v$. The agents in a set of groups see the same history. They get ``lucky'' for some arm at the same time.\\
(iii) For each set of groups in level $l-1$, agents in level $l$ see the history of agents in one of these groups. Therefore, for each arm $a$, we just need one set of groups in level $l-1$ to get ``lucky'' and then all agents in level $l$ will see enough pulls of arm $a$.

>>>>

\section{$L$-level Recommendation Policy}
\label{sec:llevel}
In this section, we give an overview of how we extend our 3-level policy to an $L$-level policy for $L > 3$ in order to achieve better regret. In Theorem \ref{thm:llevel-1}, we show our $L$-level policy. We can achieve nearly optimal regret $O(T^{1/2} polylog(T))$ with $O(\log\log(T))$ levels.
\begin{theorem}
\label{thm:llevel-1}
For any $L > 3$, we have an $L$-level recommendation policy with regret \\$O\left(T^{2^{L-1}/(2^L-1)} polylog(T) \right)$. In particular, we have an $O(\log\log(T))$-level recommendation policy with regret $O(T^{1/2} polylog(T))$. 
\end{theorem}

In Theorem \ref{thm:llevel-2}, we show a recommendation policy with instance-dependent regret guarantee. This policy has the same structure as the one in Theorem \ref{thm:llevel-1} but different parameters. Its regret depends on $\Delta$ which is the difference between the largest mean and second largest mean of arms and its construction does not depend on $\Delta$. Its regret bound outperforms the one in Theorem \ref{thm:llevel-1} when $\Delta$ is much bigger than $T^{-1/2}$. The only downside is that this policy requires more levels, i.e. $O(\log(T)/\log\log(T))$ levels. It also has the property that each agent observes a good fraction of history till its round.

\begin{theorem}
\label{thm:llevel-2}
 We have an $O(\log(T)/\log\log(T))$-level recommendation policy with regret \\$O(\min(1/\Delta, T^{1/2})polylog(T))$. Here $\Delta$ is the difference between the largest mean and second largest mean of arms. The recommendation policy does not depend on $\Delta$. Moreover, agent in round $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$. 
\end{theorem}

@@

Simply generalizing this idea to an $L$-level policy would give us a $S$-ary tree like structure and the first level will have $S^{L-1}$ groups. It incurs an extra $S^{\Omega(L)}$ factor in the regret. If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor super poly-logarithmic. If we use $\log(T)/\log\log(T)$ levels as in Theorem \ref{thm:llevel-2}, this factor goes up to polynomial in $T$.

@@

For each level, our $L$-level policy has $S^2$ groups for some $S = \Theta(\log(T))$. The groups in the $l$-th level are labeled as $G_{l,u,v}$ for $u,v\in[S]$. For any $l \in \{2,...,L\}$ and $u,v,w\in [S]$, agents in group $G_{l,u,v}$ see the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level). This connecting structure has three nice properties: \\
(i) The number of groups does not grow with $L$ and stays as $S^2 = \Theta(\log^2(T))$ in each level. Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\
(ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,S,v}$ (e.g. $G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l-1$ and $v$. The agents in a set of groups see the same history. They get ``lucky'' for some arm at the same time.\\
(iii) For each set of groups in level $l-1$, agents in level $l$ see the history of agents in one of these groups. Therefore, for each arm $a$, we just need one set of groups in level $l-1$ to get ``lucky'' and then all agents in level $l$ will see enough pulls of arm $a$.

### 2018-11-01 llevel.tex
.
expected regret -> regret

\section{Missing Proofs of Section \ref{sec:llevel}}
\label{sec:llevel-details}
In this section, we design our $L$-level recommendation policy for $L > 3$. Similarly as Section \ref{sec:3level}, we first prove them in the case of 2 arms (Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel}). We then extend them to the case of constant number of arms (Theorem \ref{thm:constarm}).

@@

\begin{theorem}
\label{thm:llevel}
The $L$-level recommendation policy gets expected regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(S^4))$. In particular, if we pick $L = \log(\ln(T)/\log(S^4))$, the expected regret is $O(T^{1/2} polylog(T))$. 
\end{theorem}

@@

By union bound, the intersection of these clean events (i.e. $\bigcap_{i=1}^4 W_i$) happens with probability $1-O(1/T)$. When this intersection does not happen, since the probability is $O(1/T)$, it cost expected regret $O(1/T) \cdot T = O(1)$.

Now we assume the intersection of clean events happens and prove upper bound on the expected regret.

@@

By Claim \ref{clm:l2_exploit}, we know that the expected regret conditioned the intersection of clean events is at most 
\begin{align*}
&\max\left( T_1\GdT S^2 , \max_{l \geq 2} \varepsilon_{l-1}S(T_1\GdT S^2 + T_2 S^3 + \cdots + T_lS^3)\right) \\
\leq & \max\left( T_1\GdT S^2 , \max_{l \geq 2} 2 \varepsilon_{l-1} T_l S^4 \right)\\
= &O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right).
\end{align*}
\end{proof}

@@

\begin{corollary}
\label{cor:llevel}
With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets expected regret $O(\min(1/\Delta, T^{1/2})polylog(T))$. Here $\Delta = |\mu_1 -\mu_2|$ and the $L$-level recommendation policy does not need to know $\Delta$. Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$. 
\end{corollary}

@@

Recall in the proof of Theorem \ref{thm:llevel}, $\varepsilon_l =\Theta(1/\sqrt{T_l S})$ for $l \in [L-1]$ and $\varepsilon_0 = 1$. Consider two cases:
\begin{itemize}
\item $\Delta < \varepsilon_{L-1} S$. In this case, notice that even always picking the sub-optimal arm gives expected regret at most $T(\mu_1-\mu_2) = T\Delta = O(T^{1/2} polylog(T))$. On the other hand, $T^{1/2} = O(polylog(T)/\Delta)$. Therefore, the expected regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
\item $\Delta \geq \varepsilon_{L-1} S$. In this case, we can find $l \in \{2,...,L\}$ such that $\varepsilon_{l-1} S\leq \Delta < \varepsilon_{l-2} S$. By Claim \ref{clm:l2_exploit}, we can upper bound the expected regret by
\begin{align*}
&\Delta \cdot (T_1 \GdT S^2  +T_2 S^3+ \cdots T_{l-1} S^3)\\
=& O(\Delta T_{l-1}S^3) \\
=&O(\Delta T_{l-2}S^7) \\
=&O(\Delta\cdot  \frac{1}{\varepsilon^2_{l-2}}\cdot S^6)\\
=&O(\Delta \cdot \frac{1}{\Delta^2}\cdot S^8)\\
=&O(polylog(T)/\Delta).
\end{align*}
We also have $1/\Delta \leq 1/(\varepsilon_{L-1}S)= O(T^{1/2})$. Therefore, the expected regret is \\$O(\min(1/\Delta, T^{1/2})polylog(T))$.
\end{itemize}

@@

\xhdr{Proof Sketch.}
We still wlog assume arm 1 has the highest mean (i.e. $\mu_1 \geq \mu_a, \forall a \in \A$. We first extend the clean events (i.e. $W_1,W_2,W_3,W_4$) in Theorem \ref{thm:llevel} to the case when $K$ is larger than 2. $W_1$ and $W_2$ extend naturally: we still set $W_1 = \bigcap_{a,s}W_1^{a,s}$ and $W_2 = \bigcap_{t,a,t_1,t_2} W_2^{t,a,t_1,t_2}$. The difference is that now $a$ is taken over $K$ arms instead of 2 arms. For $W_3$, we change the definition $W_3^{l,a} = \bigcup_u \left(W_3^{l,u,a,high}  \cap \left(\bigcap_{a' \neq a} W_3^{l,u,a',low}\right) \right)$ and $W_3 = \bigcap_{l,a} W_3^{l,a}$. We extend $W_4$ in a similar way: define $W^{a}_4$ as $\bigcup_u \left(W_4^{u,a,high} \cap \left(\bigcap_{a' \neq a} W_4^{u,a',low}\right) \right)$ and $W_4 = \bigcap_a W^a_4$. Since $K$ is a constant, it's easy to check that the same proof technique shows that the intersection of these clean events happen with probability  $1-O(1/T)$. So the case when some clean event does not happen contributes $O(1)$ to the expected regret.

@@

Finally we proceed to bound the expected regret conditioned on the intersection of clean events happens. The proofs of Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel} bound it by consider the regret from pulling the suboptimal arm (i.e. arm 2). When extending to more than 2 arms, we can do the exactly same argument for all arms except arm 1. This will blow up the expected regret by a factor of $(K-1)$ which is a constant.
\qed

>>>>

\section{Proofs of Section \ref{sec:llevel}}
\label{sec:llevel-details}
In this section, we design our $L$-level recommendation policy for $L > 3$. Similarly as Section \ref{sec:3level}, we first prove them in the case of 2 arms (Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel}). We then extend them to the case of constant number of arms (Theorem \ref{thm:constarm}).

@@

\begin{theorem}
\label{thm:llevel}
The $L$-level recommendation policy gets regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(S^4))$. In particular, if we pick $L = \log(\ln(T)/\log(S^4))$, the regret is $O(T^{1/2} polylog(T))$. 
\end{theorem}

@@

By union bound, the intersection of these clean events (i.e. $\bigcap_{i=1}^4 W_i$) happens with probability $1-O(1/T)$. When this intersection does not happen, since the probability is $O(1/T)$, it contributes $O(1/T) \cdot T = O(1)$ to the regret.

Now we assume the intersection of clean events happens and prove upper bound on the regret.

@@

By Claim \ref{clm:l2_exploit}, we know that the regret conditioned the intersection of clean events is at most 
\begin{align*}
&\max\left( T_1\GdT S^2 , \max_{l \geq 2} \varepsilon_{l-1}S(T_1\GdT S^2 + T_2 S^3 + \cdots + T_lS^3)\right) \\
\leq & \max\left( T_1\GdT S^2 , \max_{l \geq 2} 2 \varepsilon_{l-1} T_l S^4 \right)\\
= &O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right).
\end{align*}
\end{proof}

@@

\begin{corollary}
\label{cor:llevel}
With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets regret $O(\min(1/\Delta, T^{1/2})polylog(T))$. Here $\Delta = |\mu_1 -\mu_2|$ and the $L$-level recommendation policy does not need to know $\Delta$. Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$. 
\end{corollary}

@@

Recall in the proof of Theorem \ref{thm:llevel}, $\varepsilon_l =\Theta(1/\sqrt{T_l S})$ for $l \in [L-1]$ and $\varepsilon_0 = 1$. Consider two cases:
\begin{itemize}
\item $\Delta < \varepsilon_{L-1} S$. In this case, notice that even always picking the sub-optimal arm gives expected regret at most $T(\mu_1-\mu_2) = T\Delta = O(T^{1/2} polylog(T))$. On the other hand, $T^{1/2} = O(polylog(T)/\Delta)$. Therefore, the regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
\item $\Delta \geq \varepsilon_{L-1} S$. In this case, we can find $l \in \{2,...,L\}$ such that $\varepsilon_{l-1} S\leq \Delta < \varepsilon_{l-2} S$. By Claim \ref{clm:l2_exploit}, we can upper bound the regret by
\begin{align*}
&\Delta \cdot (T_1 \GdT S^2  +T_2 S^3+ \cdots T_{l-1} S^3)\\
=& O(\Delta T_{l-1}S^3) \\
=&O(\Delta T_{l-2}S^7) \\
=&O(\Delta\cdot  \frac{1}{\varepsilon^2_{l-2}}\cdot S^6)\\
=&O(\Delta \cdot \frac{1}{\Delta^2}\cdot S^8)\\
=&O(polylog(T)/\Delta).
\end{align*}
We also have $1/\Delta \leq 1/(\varepsilon_{L-1}S)= O(T^{1/2})$. Therefore, the regret is $O(\min(1/\Delta, T^{1/2})polylog(T))$.
\end{itemize}

@@

\xhdr{Proof Sketch.}
We still wlog assume arm 1 has the highest mean (i.e. $\mu_1 \geq \mu_a, \forall a \in \A$. We first extend the clean events (i.e. $W_1,W_2,W_3,W_4$) in Theorem \ref{thm:llevel} to the case when $K$ is larger than 2. $W_1$ and $W_2$ extend naturally: we still set $W_1 = \bigcap_{a,s}W_1^{a,s}$ and $W_2 = \bigcap_{t,a,t_1,t_2} W_2^{t,a,t_1,t_2}$. The difference is that now $a$ is taken over $K$ arms instead of 2 arms. For $W_3$, we change the definition $W_3^{l,a} = \bigcup_u \left(W_3^{l,u,a,high}  \cap \left(\bigcap_{a' \neq a} W_3^{l,u,a',low}\right) \right)$ and $W_3 = \bigcap_{l,a} W_3^{l,a}$. We extend $W_4$ in a similar way: define $W^{a}_4$ as $\bigcup_u \left(W_4^{u,a,high} \cap \left(\bigcap_{a' \neq a} W_4^{u,a',low}\right) \right)$ and $W_4 = \bigcap_a W^a_4$. Since $K$ is a constant, it's easy to check that the same proof technique shows that the intersection of these clean events happen with probability  $1-O(1/T)$. So the case when some clean event does not happen contributes $O(1)$ to the regret.

@@

Finally we proceed to bound the regret conditioned on the intersection of clean events happens. The proofs of Theorem \ref{thm:llevel} and Corollary \ref{cor:llevel} bound it by consider the regret from pulling the suboptimal arm (i.e. arm 2). When extending to more than 2 arms, we can do the exactly same argument for all arms except arm 1. This will blow up the regret by a factor of $(K-1)$ which is a constant.
\qed
